A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-07-19 paper.tex
getting ready for submission

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; sequence-form; approximate Nash equilibrium; primal-dual
algoithm; convex-optimization; enlarged subgradient

@@

\subsection{Notation and terminology}
\paragraph{\textbf{General notions.}}
Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
of all subsets of $X$, or equivalently the set of all binary
functions on $X$. Let $m$ and $n$ be positive integers. Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  $\|z\|$ denotes the
$2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{\langle z,
  z\rangle}$. $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the
point-wise maximum of $z$ with $0$. For example, $((-2, \pi))_+ =
(max(-2, 0), max(\pi, 0)) = (0, \pi)$. The operator $(.)_+$ is the
well-known (multi-dimensional) \textit{ramp} function. The
$n$-simplex denoted $\Delta_n$, is defined by $\Delta_n := \{z \in
\mathbb{R}^n_+|z_0 + z_1 + ... z_{n - 1} = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph{\textbf{Convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

\subsection{Statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

%\subsection{Characterization of equilibria}
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
\langle y, A^Tx  + E_2^Tq\rangle = 0.
\label{eq:feasibility}
\end{equation}

@@

@@

\begin{remark}  
It should be noted that for the class of games considered here
(sequential games with imcomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP solvers can handle. See
\cite{hoda2010smoothing}.

\end{remark}

Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice (indeed, this system of problems is NP-hard
\cite{koller1992complexity}) and such a
precision doesn't have any fundamental practical advantage. Instead, it is
customary compute so-called Nash $\epsilon$-equlibria.

@@

Let us introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.

@@

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
there exists a perturbation vector $v^*$ such that
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*).
\end{eqnarray}

@@

The above definition is a generalization of the notion of Nash
equilibria since:
\begin{itemize}
\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
\item Nash $\epsilon$-equilibria (in the sense of Definition
  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
\end{itemize}

\paragraph{Matrix games on simplexes.} It should be noted that any
matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
  game with payoff matrix $A$, for which each player's strategy
profile is a simplex; this simplex can be written in the form
\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game.  Thus the
results presented in this manuscript can be trivially applied such
games in particular. Here, the polyhedral strategy profiles $Q_k$
defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
and the primal-dual gap function $G(x,y)$ writes $G(x, y) =
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
}}(A^Tx)_i$.

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
  \epsilon$)-equilibria for sequential two-person zero-sum games with
  imcomplete information and perfect recall.

@@

@@

Then a quadruplet $(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$ solves the Nash equilibrium LCPs
  \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
  \label{thm:pd}
\end{theorem}

\begin{proof}
Note that $dom(g_1) = S_1$ and $dom(g_2) = S_2$ and observe that since the
equilibria of the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, and
the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
q) \in S_1 \times S_2$, the primal-dual gap between the primal
LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
$a(x,y)$, can be computed as
\begin{eqnarray*}
  \begin{aligned}
    a(y,p) &= \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
    i_{E_2y = e_2}\\
    &= g_1(y,p) + \underset{x' \geq
      0}{\text{max}}\text{ }\langle x',Ay - E_1^Tp\rangle +
    \underset{q'}{\text{max}}\text{ }\langle q',E_2y - e_2\rangle\\
    &= g_1(y,p) + \underset{x',
      q'}{\text{max}}\text{ }\langle x',Ay\rangle - \langle x',
    E_1^Tp\rangle + \langle q',E_2y\rangle -
    (i_{x' \ge 0} + \langle e_2,q\rangle)\\
    &= g_1(y,p)
      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
      q') = g_1(y,p)
      - \underbrace{\underset{x',q'}{\text{min}}\text{
        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)},
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}

Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
-\langle q, e_2\rangle -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
 i_{E_1x = e_1}\\
 &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }\langle y', A^Tx + E_2^Tq\rangle +
 \underset{p'}{\text{min}}\text{ }\langle p', e_1-E_1x\rangle\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{min}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q)
 +\underbrace{\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p',
   x, q)}_{\phi_1(x, q)}.
   \end{aligned}
\end{eqnarray*}
Thus, noting that $-\infty \le \phi_1(x, q), \phi_2(y, p), < +\infty$,
one computes the primal-dual gap between the primal LCP
\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.
\end{proof}

@@

\subsection{Algorithm and convergence rate}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, there exists an index
$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
error bounds hold:
\begin{eqnarray}
\|\tilde{v}_a^{k_0}\| \le \rho \text{ and }
\|\tilde{\epsilon}_a^{k_0}\| \le \epsilon
\end{eqnarray}

>>>>

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; approximate Nash equilibrium; primal-dual
algoithm; convex-optimization

@@

\subsection{Notation, terminology, and some aspects of modern convex analysis}
\paragraph{\textbf{General notions.}}
Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
of all subsets of $X$, or equivalently the set of all binary
functions on $X$. Let $m$ and $n$ be positive integers. Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  $\|z\|$ denotes the
$2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{\langle z,
  z\rangle}$. $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the
point-wise maximum of $z$ with $0$. For example, $((-2, \pi))_+ =
(max(-2, 0), max(\pi, 0)) = (0, \pi)$. The operator $(.)_+$ is the
well-known (multi-dimensional) \textit{ramp} function. The
$n$-simplex denoted $\Delta_n$, is defined by $\Delta_n := \{z \in
\mathbb{R}^n_+|z_0 + z_1 + ... z_{n - 1} = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph{\textbf{Modern convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

\subsection{Nash-equilibrium concepts and statement of the problem}
\subsubsection{Preliminaries}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
\langle y, A^Tx  + E_2^Tq\rangle = 0.
\label{eq:feasibility}
\end{equation}

@@

\subsubsection{A note about matrix games on simplexes.} It should be
noted
that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
  game with payoff matrix $A$, for which each player's strategy
profile is a simplex; this simplex can be written in the form
\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game.  Thus the
results presented in this manuscript can be trivially applied such
games in particular. Here, the polyhedral strategy profiles $Q_k$
defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
and the primal-dual gap function $G(x,y)$ writes
\begin{eqnarray}G(x, y) =
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
}}(A^Tx)_i.
\end{eqnarray}

@@

\subsubsection{Approximate feasibility and optimality}
Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice (indeed, this system of problems is NP-hard
\cite{koller1992complexity}) and such a precision doesn't have any
fundamental practical advantage. Instead, it is customary compute
``approximate'' Nash equilibria.

@@

Let us now, introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.

@@

\begin{definition}[\textbf{Nash $(\epsilon_1,\epsilon_2)$-equilibria}]
Given tolerance levels $\epsilon_1, \epsilon_2 > 0$, a Nash
$(\epsilon_1,\epsilon_2)$-equilibrium for the GSP \eqref{eq:unconstrained_pb}
is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
there exists a perturbation vector $v^*$ such that
\begin{eqnarray}
\|v^*\| \le \epsilon_1 \text{ and}\hspace{.5em} v^* \in
\partial_{\epsilon_2}[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, ., .)](y^*,p^*,x^*,q^*).
\end{eqnarray}

@@

The above definition is a generalization of the notion of Nash
equilibria since:
\begin{itemize}
\item Exact Nash equilibria correspond to Nash $(0,0)$-equilibria.
\item Nash $\epsilon$-equilibria (in the sense of Definition
  \ref{thm:approx_nash}) correspond to Nash $(0,\epsilon)$-equilibria.
\end{itemize}

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\epsilon)$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\epsilon,
  0)$-equilibria in sequential two-person zero-sum games with
  imcomplete information and perfect recall.

@@

Finally, let us note that for the class of games considered here
(sequential games with imcomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP and interior-point solvers can
handle. See for example \cite{hoda2010smoothing}.

@@

Then a quadruplet $(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$ solves the Nash equilibrium LCPs
  \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$). In order words, GSP($\Psi_1$,
  $\Psi_2$, $g_1$, $g_2$) is equivalent to the Nash equilibrium LCPs
  \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.
  \label{thm:pd}
\end{theorem}

\begin{proof}
Note that $dom(g_1) = S_1$ and $dom(g_2) = S_2$ and observe that since the
equilibria of the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb}, and
the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
q) \in S_1 \times S_2$, the primal-dual gap between the primal
LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
$a(x,y)$, can be computed as
\begin{eqnarray*}
  \begin{aligned}
    a(y,p) &= \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
    i_{E_2y = e_2}\\
    &= g_1(y,p) + \underset{x' \geq
      0}{\text{max}}\text{ }\langle x',Ay - E_1^Tp\rangle +
    \underset{q'}{\text{max}}\text{ }\langle q',E_2y - e_2\rangle\\
    &= g_1(y,p) + \underset{x',
      q'}{\text{max}}\text{ }\langle x',Ay\rangle - \langle x',
    E_1^Tp\rangle + \langle q',E_2y\rangle -
    (i_{x' \ge 0} + \langle e_2,q\rangle)\\
    &= g_1(y,p)
      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
      q') = g_1(y,p)
      - \underbrace{\underset{x',q'}{\text{min}}\text{
        }\hat{\Psi}_2(y, p, x', q')}_{\phi_2(y,p)}\\
      &= g_1(y, p) - \phi_2(y, p).
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}

Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
-\langle q, e_2\rangle -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
 i_{E_1x = e_1}\\
 &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }\langle y', A^Tx + E_2^Tq\rangle +
 \underset{p'}{\text{min}}\text{ }\langle p', e_1-E_1x\rangle\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{min}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q)
 +\underbrace{\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p',
   x, q)}_{\phi_1(x, q)}\\
 &= -g_2(x, q) + \phi_1(x, q). 
   \end{aligned}
\end{eqnarray*}
Thus, noting that $-\infty \le \phi_1(x, q), \phi_2(y, p), < +\infty$
(so that all the operations below are valid),
one computes the primal-dual gap between the primal LCP
\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the zero-sum condition $\Psi_1 + \Psi_2
:= 0$.
\end{proof}

@@

\subsection{Algorithm and convergence rate}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/\epsilon)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$, there exists an index
$k_0 \le \frac{2d_0\|K\|}{\epsilon}$ such that after $k_0$ iterations
the algorithm produces the following a quadruplet
$(y^{k_0},p^{k_0},x^{k_0},q^{k_0})$ and a vector $v^{k_0}$ such that
\begin{eqnarray}
\|v^{k_0}\| \le \epsilon \text{ and}\hspace{.5em} v^{k_0} \in
\partial[\hat{\Psi}_1(., ., x^{k_0}, q^{k_0}) +
  \hat{\Psi}_2(y^{k_0}, p^{k_0}, ., .)](y^{k_0},p^{k_0},x^{k_0},q^{k_0}).
\end{eqnarray}
